Enhanced proximity effect in zigzag-shaped Majorana Josephson junctions.

### 2019-03-06 paper/snakemajoranas.tex
consistent E_z usage

%%██████████████████████████████████████████████████████████████████████████
%%██ Introduction
%%██████████████████████████████████████████████████████████████████████████
\section{Introduction}
\comment{Hybrid NS structures become topological and are useful for TQC.}
A hybrid structure containing a semiconductor with strong spin-orbit coupling coupled to a superconductor, inside a magnetic field becomes topological within the right parameter regime ($E_z^2>\mu^2+\Delta^2$ for a simple nanowire), and Majorana bound states appear on its edges~\cite{Lutchyn2010,Oreg2010}.
Majorana bound states are a promising candidate to form the basis of a stable platform for topological quantum computing. ~\cite{Alicea2012,Beenakker2013,Beenakker2016,Leijnse2012}
The current experimental effort ~\cite{Mourik2012,Das2012,Deng2012,Churchill2013,Zhang2018} focuses on creating pairs of Majorana bound states in hybrid normal-superconductor (NS) nanowire structures.

@@

\comment{We consider a two-dimensional system with zigzag and BdG Hamiltonian.}
We consider a Josephson junction (Fig.~\ref{fig:setup}) consisting of a 2D strip of semiconductor, with superconductors on both sides.
We modulate the shape of the normal region, which can be either zigzag as depicted [Fig.~\ref{fig:setup}(b)], or a more smooth sinusoidal-like shape.
Similar to the conventional straight system \cite{Pientka2017}, a magnetic field $B_x$ perpendicular to the junction is applied.
We model the system with a Bogoliubov-de Gennes Hamiltonian (BdG):
\begin{subequations}
\begin{align}
    H_\textrm{N} = & \left[\frac{\hbar^2\left(\kx^2 + \ky^2\right)}{2\meff} - \mu + \alpha \left( \ky \sigma_x - \kx \sigma_y \right) \right] \tau_z
        + E_\text{z} \sigma_x, \\
    H_\textrm{SC} = & \left[\frac{\hbar^2\left(\kx^2 + \ky^2\right)}{2\meff} - \mu\right] \tau_z
        + \Delta \cos{\frac{\phi}{2}} \tau_x + \Delta \sin{\frac{\phi}{2}} \tau_y.
\end{align}
\label{eq:hamiltonian}
\end{subequations}
Here $H_\textrm{N}$ and $H_\textrm{SC}$ are the Hamiltonians of the semiconductor and superconductors, respectively.
The normal part has a linear Rashba spin-orbit coupling term with strength $\alpha$ and a Zeeman field with $E_z=\frac{1}{2} \mu_B g B_x$.
The superconductor has a coupling term $\Delta$, and the phases of the superconductors equal to $\pm\phi/2$.
Both the normal part and the superconductors have a kinetic term and chemical potential $\mu$.
The BdG Hamiltonian acts on the spinor wave function $\Psi={\left(\psi_{e\uparrow},\psi_{e\downarrow},\psi_{\textrm{h}\downarrow},-\psi_{\textrm{h}\uparrow}\right)}^{T}$, where $\psi_e$, $\psi_\textrm{h}$ are its electron and hole components, and $\psi_\uparrow$, $\psi_\downarrow$ are the spin-up and spin-down components.
The Pauli matrices $\sigma_{i}$ act on the spin degree of freedom and $\tau_{i}$ act on the electron-hole degree of freedom.
We consider a zigzag pattern with a period $z_x$, a peak-to-peak amplitude $z_y$, and $W$ the width of the junction [see Fig.~\ref{fig:setup}(b)].
Later we relax this assumption and show that the exact shape is unimportant.

>>>>

%%██████████████████████████████████████████████████████████████████████████
%%██ Introduction
%%██████████████████████████████████████████████████████████████████████████
\section{Introduction}
\comment{Hybrid NS structures become topological and are useful for TQC.}
A hybrid structure containing a semiconductor with strong spin-orbit coupling coupled to a superconductor, inside a magnetic field becomes topological within the right parameter regime ($E_\text{Z}^2>\mu^2+\Delta^2$ for a simple nanowire), and Majorana bound states appear on its edges~\cite{Lutchyn2010,Oreg2010}.
Majorana bound states are a promising candidate to form the basis of a stable platform for topological quantum computing. ~\cite{Alicea2012,Beenakker2013,Beenakker2016,Leijnse2012}
The current experimental effort ~\cite{Mourik2012,Das2012,Deng2012,Churchill2013,Zhang2018} focuses on creating pairs of Majorana bound states in hybrid normal-superconductor (NS) nanowire structures.

@@

\comment{We consider a two-dimensional system with zigzag and BdG Hamiltonian.}
We consider a Josephson junction (Fig.~\ref{fig:setup}) consisting of a 2D strip of semiconductor, with superconductors on both sides.
We modulate the shape of the normal region, which can be either zigzag as depicted [Fig.~\ref{fig:setup}(b)], or a more smooth sinusoidal-like shape.
Similar to the conventional straight system \cite{Pientka2017}, a magnetic field $B_x$ perpendicular to the junction is applied.
We model the system with a Bogoliubov-de Gennes Hamiltonian (BdG):
\begin{subequations}
\begin{align}
    H_\textrm{N} = & \left[\frac{\hbar^2\left(\kx^2 + \ky^2\right)}{2\meff} - \mu + \alpha \left( \ky \sigma_x - \kx \sigma_y \right) \right] \tau_z
        + E_\text{Z} \sigma_x, \\
    H_\textrm{SC} = & \left[\frac{\hbar^2\left(\kx^2 + \ky^2\right)}{2\meff} - \mu\right] \tau_z
        + \Delta \cos{\frac{\phi}{2}} \tau_x + \Delta \sin{\frac{\phi}{2}} \tau_y.
\end{align}
\label{eq:hamiltonian}
\end{subequations}
Here $H_\textrm{N}$ and $H_\textrm{SC}$ are the Hamiltonians of the semiconductor and superconductors, respectively.
The normal part has a linear Rashba spin-orbit coupling term with strength $\alpha$ and a Zeeman field with $E_\text{Z}=\frac{1}{2} \mu_B g B_x$.
The superconductor has a coupling term $\Delta$, and the phases of the superconductors equal to $\pm\phi/2$.
Both the normal part and the superconductors have a kinetic term and chemical potential $\mu$.
The BdG Hamiltonian acts on the spinor wave function $\Psi={\left(\psi_{e\uparrow},\psi_{e\downarrow},\psi_{\textrm{h}\downarrow},-\psi_{\textrm{h}\uparrow}\right)}^{T}$, where $\psi_e$, $\psi_\textrm{h}$ are its electron and hole components, and $\psi_\uparrow$, $\psi_\downarrow$ are the spin-up and spin-down components.
The Pauli matrices $\sigma_{i}$ act on the spin degree of freedom and $\tau_{i}$ act on the electron-hole degree of freedom.
We consider a zigzag pattern with a period $z_x$, a peak-to-peak amplitude $z_y$, and $W$ the width of the junction [see Fig.~\ref{fig:setup}(b)].
Later we relax this assumption and show that the exact shape is unimportant.
